---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# tdar

This package allows programmatic access to 
[the Digital Archaeological Record (tDAR)](https://www.tdar.org), a service of [Digital Antiquity](https://www.digitalantiquity.org).

## Installation

You can install tdar from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("bocinsky/tdar")
```

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

## Basic usage
### Authentication
tDAR authentication is handled through a username and password.
Log in using the `tdar::tdar_login` function

```{r tdar-login, eval = FALSE}
tdar::tdar_login(tdar_user = '<your username>', 
                 tdar_password = '<your password>')
```

The `tdar::tdar_login` function automatically searches for a stored tDAR user name and password in your environment. 
If you have a username and password, pass them in as environment vars using:

```{r tdar-env, eval = FALSE}     
Sys.setenv(tdar_un = '<your username>',
           tdar_pw = '<your password>')
```
If you do not yet have a username and password, register for one here at [https://core.tdar.org/account/new/].
To become part of the tDAR API Group, please contact the Digital Antiquity staff at [info@digitalantiquity.org].

